### 2016-07-13 Docs/managing_jobs/managingjobs.tex
more compiler note updates

@@

@@

\item Cray 8.4.3 triggers a backtrace error in {\tt make\_pi\_cc.f90}---this is 
  likely an optimization issue, and may be 2-d specific.

  Previously,  Cray 8.4.0 worked well on edison/NERSC with MPI/OpenMP.

@@

Note: in order to compile, you will need to ensure that both the {\tt
python} and {\tt python\_base} modules are loaded (via the {\tt
module} command).

>>>>

  gfortran 6.1.1 is used for nightly regression testing.

@@

There are no known issues with PGI 16.5 compilers---these are used
for nightly regression testing.

@@

\item Cray 8.4.x has worked in the past, but it has not been used
  at NERSC in a while.

@@

Note: in order to compile, you will need to ensure that both the {\tt
python} and {\tt python\_base} modules are loaded (via the {\tt
module} command).  \MarginPar{this may have changed with the migration of NERSC to anaconda?}
